### 2017-05-30 sheets/basis-3/sheet-basis-3.tex
Fix exercise 3.6

\begin{answer}
  We have to give two functors
  $H \from \ftrcat{\cat{A}^\op}{\cat{B}^\op} \to \ftrcat{\cat{A}}{\cat{B}}^\op$
  and
  $J \from \ftrcat{\cat{A}}{\cat{B}}^\op \to \ftrcat{\cat{A}^\op}{\cat{B}^\op}$
  such that $H \circ J = 1_{\ftrcat{\cat{A}}{\cat{B}}^\op}$ and $J \circ H = 1_{\ftrcat{\cat{A}^\op}{\cat{B}^\op}}$.

  First we define $H$. For that we first map objects of
  $\ftrcat{\cat{A}^\op}{\cat{B}^\op}$ (being itself functors from $\cat{A}^\op$ to $\cat{B}^\op$)
  to objects of $\ftrcat{\cat{A}}{\cat{B}}^\op$ (being itself functors from $\cat{A}$ to $\cat{B}$).

  Let $F\from \cat{A}^\op \to \cat{B}^\op$ be an object of $\ftrcat{\cat{A}^\op}{\cat{B}^\op}$.
  Because every object $A : \cat{A}^\op$ is also an object of $\cat{A}$ we can define
  $H(F)(A) := F(A)$.
  Now let $f \from A \to B$ be an morphism in $\cat{A}^\op$. We have $F(f^\op)=g^\op$ for some morphism $g$ in $\cat{B}^\op$.
  We define $H(F)(f) := F(f^\op)^\op = g$.

  Now let $F, G \from \cat{A}^\op \to \cat{B}^\op$ be objects and
  $\alpha \from F \to G$ be an morphism of $\ftrcat{\cat{A}^\op}{\cat{B}^\op}$.
  $\alpha = (F(A) \stackrel{\alpha_A}{\to} G(A))_A$ is an natural transformation.
  We define $H(\alpha) := \beta \from H(G) \to H(F) := (\alpha_A^\op)_A$ and have to show that $\beta$ is indeed such a natural transformation.
  Let $A, A' : \cat{A}$ and $f \from A \to A'$. We have to show that the following diagram commutes:
  \[
    \begin{tikzcd}
      H(G)(A) \arrow{r}{H(G)(f)} \arrow{d}{H(\alpha)_A} & H(G)(A') \arrow{d}{H(\alpha)_A'} \\
      H(F)(A) \arrow{r}{H(F)(f)} & H(F)(A')
    \end{tikzcd}
  \]
  By unfolding the definition of $H$ this diagram commutes if and only if the following diagram commutes:
  \[
    \begin{tikzcd}
      G(A) & G(A') \arrow{l}{G(f^\op)} \\
      F(A) \arrow{u}{\alpha_A} & F(A') \arrow{l}{F(f^\op)} \arrow{u}{\alpha_{A'}}
    \end{tikzcd}
  \]
  This diagram commutes because $\alpha$ is a natural transformation.

  Secondly we define $J$ using a similar construction as above and get
  $H \circ J = 1_{\ftrcat{\cat{A}}{\cat{B}}^\op}$ and $J \circ H = 1_{\ftrcat{\cat{A}^\op}{\cat{B}^\op}}$.

  Now by definition of $\iso$,
  $\ftrcat{\cat{A}^\op}{\cat{B}^\op} \iso \ftrcat{\cat{A}}{\cat{B}}^\op$
  holds.
\end{answer}

@@

to a functor in such a way that $(\epsln_B)_{B \in \cat{B}}$ is a natural

@@

                    Using the naturality axiom for $\eta$ we obtain our goal.

@@

                    By analogous reasoning using $\epsln$ we obtain that $G$ is also faithful.

@@

                    Let $A, A' \in \cat{A}$ and $g \from F(A) \to F(A')$.
                    We define $f := \eta_{A'}^{-1} \circ G(g) \circ \eta_A$ and use the naturality axiom for $\eta$ in order to get:
                        G(F(f)) & = \eta_A' \circ f \circ \eta_A^{-1}\\
                                & = \eta_A' \circ \eta_{A'}^{-1} \circ G(g) \circ \eta_A \circ \eta_A^{-1}\\
                                & = G(g)
                    Since $G$ is faithful we obtain $F(f) = g$.
                    Thus $F$ is full.

@@

            For each $B \in \cat{B}$ the class of objects $A \in \cat{A}$ which fulfill $F(A) \iso B$ is non empty, because $F$ is essentially surjective on objects.
            We define $G(B)$ as such an $A$ using the axiom of choice.
            In addition we have an isomorphism $\epsln_B\from F(G(B)) \to B$.

@@

            We obtain $G(F(f)) = \eta_{A'} \circ f \circ \eta_A^{-1}$ because $F$ is faithful.

>>>>

@@

to a functor in such a way that $(\epsln)_{B \in \cat{B}}$ is a natural

@@

                    Using this commutativity for $\eta$ we obtain our goal.

@@

@@

                    %TODO

@@

            $F$ is essentially surj. on obj. so $\forall B \in \cat{B}.\, \exists A \in \cat{A}.\, F(A) \iso B$.
            We denote by $h(A, B) \from F(A) \to B$ this isomorphism.
            For each $B \in \cat{B}$ we define $G(B)$ such that $F(G(B)) \iso B$ under $h(G(B), B)$ and $\epsln_B\from F(G(B)) \to B := h(G(B), B)$.

@@

            We obtain $G(F(f)) = \eta_{A'} \circ f \circ \eta_A^{-1}$ because $F$ is faithfull.
